Wigglyhedra

### 2024-03-18 draft/wigglyhedra.tex
Added small question (typo fix?)

\begin{definition}
\label{def:cvectors}
Consider a wiggly pseudotriangulation~$T$, and label the corners as in \cref{def:bijection1}.
Consider an interior wiggly arc~$\alpha$ in a wiggly pseudotriangulation~$T$, denote by~$u$ and~$v$ the labels incident to~$\alpha$ and respectively below and above~$\alpha$, and let~$\bar u \eqdef \lceil u/2 \rceil$ and~$\bar v \eqdef \lceil v/2 \rceil$.
The \defn{$\b{c}$-vector} of~$\alpha$ in~$T$ is the vector~$\b{c}(\alpha, T)$ with coordinates
\begin{itemize}
\item $\b{c}(\alpha, T)_{2w-1} = - \b{c}(\alpha, T)_{2w} = (-1)^{w \in A} (-1)^{u>v}/4$ for all~$w$ strictly between~$\bar u$ and~$\bar v$,
\item $\b{c}(\alpha, T)_u = 1/2$ if~$\bar u = \bar v$, or if~$\bar u$ and the wiggly arcs incident to~$\bar u$ are on the same side of~$\bar u$, and $\b{c}(\alpha, T)_{2\bar u-1} = \b{c}(\alpha, T)_{2\bar u} = 1/4$ otherwise,
\item $\b{c}(\alpha, T)_v = -1/2$ if~$\bar u = \bar v$, or if~$\bar u$ and the wiggly arcs incident to~$\bar v$ are on the same side of~$\bar v$, and $\b{c}(\alpha, T)_{2\bar v-1} = \b{c}(\alpha, T)_{2\bar v} = -1/4$ otherwise,
\item $\b{c}(\alpha, T)_w = 0$ for all other coordinates.
\end{itemize}
Set~$\b{c}(T) \eqdef \set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$
\end{definition}

>>>>

\begin{definition}
\label{def:cvectors}
Consider a wiggly pseudotriangulation~$T$, and label the corners as in \cref{def:bijection1}.
Consider an interior wiggly arc~$\alpha$ in a wiggly pseudotriangulation~$T$, denote by~$u$ and~$v$ the labels incident to~$\alpha$ and respectively below and above~$\alpha$, and let~$\bar u \eqdef \lceil u/2 \rceil$ and~$\bar v \eqdef \lceil v/2 \rceil$.
The \defn{$\b{c}$-vector} of~$\alpha$ in~$T$ is the vector~$\b{c}(\alpha, T)$ with coordinates
\begin{itemize}
\item $\b{c}(\alpha, T)_{2w-1} = - \b{c}(\alpha, T)_{2w} = (-1)^{w \in A} (-1)^{u>v}/4$ for all~$w$ strictly between~$\bar u$ and~$\bar v$,
\item $\b{c}(\alpha, T)_u = 1/2$ if~$\bar u = \bar v$, or if~$\bar u$ and the wiggly arcs incident to~$\bar u$ are on the same side of~$\bar u$, and $\b{c}(\alpha, T)_{2\bar u-1} = \b{c}(\alpha, T)_{2\bar u} = 1/4$ otherwise,\asilata{In this item, should ``or if \(\bar u\) and\dots'' be ``or if \(\bar v\) and \dots''?}
\item $\b{c}(\alpha, T)_v = -1/2$ if~$\bar u = \bar v$, or if~$\bar u$ and the wiggly arcs incident to~$\bar v$ are on the same side of~$\bar v$, and $\b{c}(\alpha, T)_{2\bar v-1} = \b{c}(\alpha, T)_{2\bar v} = -1/4$ otherwise,
\item $\b{c}(\alpha, T)_w = 0$ for all other coordinates.
\end{itemize}
Set~$\b{c}(T) \eqdef \set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$
\end{definition}
